---
title: "Presentation"
author: "P. M. Cooper"
date: "June 4, 2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r, echo = FALSE}
library(tidycensus)
library(plotly)

county18<-get_acs("county",survey = "acs1", key = "993d02931a941bd1f5af535c637800916aa504b2",variables=c("B28002_001","B28002_013","S1701_C03_002"))

cty18_wide<-data.frame(county18$GEOID[county18$variable=="B28002_001"],
                       county18$NAME[county18$variable=="B28002_001"],
                       county18$estimate[county18$variable=="B28002_001"],
                       county18$estimate[county18$variable=="B28002_013"],
                       county18$estimate[county18$variable=="S1701_C03_002"])

names(cty18_wide)<-c("GEOID","NAME","TOTPOP","NOINT","POVPCT")

cty18_wide$INTPCT<- with(cty18_wide,round((1-(NOINT/TOTPOP))*100,1))

plot_ly(x=cty18_wide$POVPCT,y=cty18_wide$INTPCT, type='scatter',mode='marker')      
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

